---
title: "Data Science Project"
output: pdf_document
date: '2022-07-05'
---
Question:
WHAT ARE THE CAUSES OF DELAYED DEPARTURES AT CHICAGO O'HARE INTERNATIONAL AIRPORT???

Notes:
Time after 12 am for departure
Day of week starts on Monday representing 1
Length in minutes representing the duration of the flight

Final:
Data set for ANALYZATION of Delays on Chicago O'hare Airport Departures
-Analyze time of departure
-Analyze duration of flight
-Analyze airline of operation

Abbreviations:
Alaska Airlines(AS) 
American Airlines(AA) 
Continental Airlines(CO) 
Delta Airlines(DL) 
United Airlines (UA) 

Coding:
-How to convert time after 12 into actual time for the 'Time' column(Possibly function feature from lecture 9?)
-How to convert day of the week from numbers into actual days
-Insert summary of basic statistics
-Trends in form of graphs and charts

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
#Importing Tidyverse
library(tidyverse)
#Reading the CSV
Airlines <- read.csv("~/Desktop/Data Science Final Project/Airlines.csv", stringsAsFactors=TRUE)
#Filtering/Removing
Chicago = Airlines %>% filter(AirportFrom == "ORD")
#Selecting
Chicago = Chicago%>% select(-c("id","Flight"))
#Renaming
Chicago = Chicago %>%rename(`Depart_@` = "Time") %>%rename(`Duration` = "Length") 
#Adding column representing duration in terms of hours
Chicago = Chicago %>% mutate(Duration_Hours = Duration/60)
#Adding column representing departure time in hour format
Chicago = Chicago %>% mutate(`Depart_@Time` = `Depart_@` /60)

#Function to change numbers into strings representing days of the week
Days = function(Number){
  x = length(Number)
  result = rep(0,x)
  for(i in 1:x){
    if(Number[i] == 1){
      result[i] = "Monday"
    } else if(Number[i] == 2){
      result[i] = "Tuesday"
    } else if(Number[i] == 3){
      result[i] = "Wednesday"
    } else if(Number[i] == 4){
      result[i] = "Thursday"
    } else if(Number[i] == 5){
      result[i] = "Friday"
    } else if(Number[i] == 6){
      result[i] = "Saturday"
    } else if(Number[i] == 7){
      result[i] = "Sunday"
    }
  }
  return(result)
 }
Chicago = Chicago %>% mutate(Day_Week = Days(DayOfWeek))
```

```{r}
#Basic Summary of data
summary(Chicago)
```

```{r}
#Delay filtered sets
Delay = Chicago%>% filter(Delay == 1)
Delay = Delay %>% select(c("Airline","Delay"))
```

Airline specific delay/no delay subsets
```{r}
#Numbers of Delay per Airline
table(Delay$Airline)
length(Delay$Airline)
```

Delay/No delay tables
```{r}
#Endeavor Air Subset
`9E_Total` = Chicago%>% filter(Airline == "9E")
E_delAvg <- 43/82
#American Airlines Subset
AA_Total = Chicago%>% filter(Airline == "AA")
AA_delAvg <- 2632/4486
#Alaska Airlines Subset
AS_Total = Chicago%>% filter(Airline == "AS")
AS_delAvg <- 85/153
#JetBlue Subset
`B6_Total` = Chicago%>% filter(Airline == "B6")
B6_delAvg <- 74/180
#Continental Airlines Subset
CO_Total = Chicago%>% filter(Airline == "CO")
CO_delAvg <- 323/473
#Delta Subset
DL_Total = Chicago%>% filter(Airline == "DL")
DL_delAvg <- 300/439
#Eva Air Subset
EV_Total = Chicago%>% filter(Airline == "EV")
EV_delAvg <- 256/405
#Envoy Air Subset
MQ_Total = Chicago%>% filter(Airline == "MQ")
MQ_delAvg <- 2827/6634
#PSA Airlines Subset
OH_Total = Chicago%>% filter(Airline == "OH")
OH_delAvg <- 76/207
#Skywest Airlines Subset
OO_Total = Chicago%>% filter(Airline == "OO")
OO_delAvg <- 1720/3171
#US Airways Subset
US_Total = Chicago%>% filter(Airline == "US")
US_delAvg <- 252/587
#JSX Airlines Subset
XE_Total = Chicago%>% filter(Airline == "XE")
XE_delAvg <- 1030/2060
#Mesa Airlines Subset
YV_Total = Chicago%>% filter(Airline == "YV")
YV_delAvg <- 435/899
#United Airlines Subset
UA_Total = Chicago%>% filter(Airline == "UA")
UA_delAvg <- 1853/5046

airlines <- c("9E", "AA", "AS","B6","CO","DL","EV","MQ","OH","OO","US","XE","YV","UA")
delays <- c(E_delAvg, AA_delAvg, AS_delAvg, B6_delAvg, CO_delAvg, DL_delAvg, 
            EV_delAvg, MQ_delAvg, OH_delAvg, OO_delAvg, UA_delAvg, US_delAvg, XE_delAvg, YV_delAvg)
```

Graphs/Charts
```{r}
#Bar Plot
barplot(delays~airlines, main= "Proprotion of Delays for Different Airlines", 
        xlab="Airlines", ylab="Proportion of Delays", col=rainbow(14))
```



Day of week delay analysis
```{r}
DayofWeeks = Chicago %>% select(c("Day_Week","Delay"))
#Table of Delays per day
table(DayofWeeks$Day_Week)
length(DayofWeeks$Day_Week)
```

Number of delays per week using sampling
```{r}
#Data sets representing the delays for each day
Monday = DayofWeeks%>% filter(Day_Week == "Monday")
Tuesday = DayofWeeks%>% filter(Day_Week == "Tuesday")
Wednesday = DayofWeeks%>% filter(Day_Week == "Wednesday")
Thursday = DayofWeeks%>% filter(Day_Week == "Thursday")
Friday = DayofWeeks%>% filter(Day_Week == "Friday")
Saturday = DayofWeeks%>% filter(Day_Week == "Saturday")
Sunday = DayofWeeks%>% filter(Day_Week == "Sunday")
```

```{r}
#Sampling delays for each day
set.seed(143572)
sampleMon = Monday[sample(nrow(Monday), size = 429, replace = FALSE),]
sampleMonDel = sampleMon %>% filter(Delay == 1)
Mon_del <- 223
sampleTues = Tuesday[sample(nrow(Tuesday), size = 429, replace = FALSE),]
sampleTuesDel = sampleTues %>% filter(Delay == 1)
Tues_del <- 203
sampleWed = Wednesday[sample(nrow(Wednesday), size = 429, replace = FALSE),]
sampleWedDel = sampleWed %>% filter(Delay == 1)
Wed_del <- 225
sampleThurs = Thursday[sample(nrow(Thursday), size = 429, replace = FALSE),]
sampleThursDel = sampleThurs %>% filter(Delay == 1)
Thurs_del <- 217
sampleFri = Friday[sample(nrow(Friday), size = 429, replace = FALSE),]
sampleFriDel = sampleFri %>% filter(Delay == 1)
Fri_del <- 195
sampleSat = Saturday[sample(nrow(Saturday), size = 429, replace = FALSE),]
sampleSatDel = sampleSat %>% filter(Delay == 1)
Sat_del <- 246
sampleSun = Sunday[sample(nrow(Sunday), size = 429, replace = FALSE),]
sampleSunDel = sampleSun %>% filter(Delay == 1)
Sun_del <- 183

#Combining into single sample
sampleStr  <- c(Mon_del, Tues_del, Wed_del, Thurs_del, Fri_del, Sat_del, Sun_del)
sampleStr
```

Plotting days per week delays
```{r}
barplot(sampleStr,main = "Delays per Day", names.arg = c("Mon", "Tues", "Wed", "Thurs", "Fri","Sat", "Sun"), col = rainbow(7), xlab = "Days", ylab = "Number of delays")
```



  Time of Departure Delay Analysis
```{r}
time = Chicago %>% select("Depart_@Time", "Delay")
time = time %>% filter(Delay == 1)
```

```{r}
tot_Times = data.frame(table(time$`Depart_@Time`)) 
tot_Times$Var2 = as.numeric(as.character(tot_Times$Var1))

plot(tot_Times$Var2,tot_Times$Freq, xlab = "Time of Departure", ylab = "Number of delays", main = "Scatter Plot Time of Deprture Times vs Number of delays", pch = 19, col = "dark salmon")
```