---
title: "Lab Expected CLT"
author: "Abhi Thanvi, Paul Holaway"
date: "July 11th, 2022"
output: pdf_document
toc: True
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
\newpage

# Lab Expected CLT

## Welcome

Just like learning a new spoken language, you will not learn the language without practice. Labs are an important part of this course. Collaboration on labs is **extremely encouraged**. If you find yourself stuck for more than a few minutes, ask a neighbor or course staff for help. When you are giving help to your neighbor, explain the **idea and approach** to the problem without sharing the answer itself so they can figure it out on their own. This will be better for them and for you. For them because it will stick more and they will have a better understanding of the concept. For you because if you can explain it to other students, that means you understand it better too.

## The Idea of this Lab

The idea behind this lab is the importance of Central Limit Theorem and Random Variable. Central Limit Theorem (aka CLT) is the basis of lot of the statistical inference procedures that you will see later in this course. In other words, CLT allows us to do a lot of the statistics we do today. Random Variable is a tool for statisticians to approximate the distribution of our sample and calculate certain attributed about our sample. What we learned today and apply in this lab might seem like an abstract or ["random"](https://www.youtube.com/watch?v=9rIy0xY99a0) topic (haha random), but trust me that these topics are important for becoming a good statisticians, and eventually a even better data scientist.

  **"Randomness in statistics, if done many times and correctly, can show patterns!" -  Woke Abhi**

## Problem 1: Central Limit Theorem (CLT)

**Question 1:** Among your group, discuss what is Central Limit Theorem? Report an answer in your own words.

**Answer:** (Student Response Here) Central Limit Theorem (aka CLT) is if you randomly sample from any population, the distributions of the sample means will be approximately be normally distributed. Your answer may vary, but should be something along this line. 

**Question 2:** If you have a gamma distribution, and you sample it 1000 times. What distribution will it most likely follow and why?

**Answer:** (Student Response Here) Normal Distribution using CLT.

\newpage
## Problem 2: Random Variable (RV)

**Question 1:** Let's suppose you are playing a game with a friend called Winner Takes All. You win the game if you roll an odd number, but lose an even number. What would the expected number and standard deviation of wins be if you rolled 3 times?

**Answer:**
$$
\mathbb{E}(Win)=3*P(Win)=3*\frac{1}{2}=1.5
$$
$$
SD(Win)=\sqrt{3*P(Win)P(Lose)}={}\sqrt{3*\frac{1}{2}*\frac{1}{2}}=\sqrt{\frac{3}{4}}\approx0.8660
$$

**Question 2:** A major IT company makes some really cool gadgets. One out of every 50 gadgets is faulty, but the company doesn't know which ones are faulty until a buyer complains. Suppose the company makes a *$5* profit on the sale of a working gadget. The downside is that the company loses *$60* for every faulty gadget because the customers return the product and they have to repair it. Will the company make a profit for long term?

*Hint: What does Expected Value mean? What does Standard Deviation mean?*

**Answer:** $\mathbb{E}(X)$ Will show us the profit or loss of the company over long term.
            $E(X) = \frac{49}{50} * 5 + \frac{1}{50} * (-60) = 4.9 - 1.2 = 3.7$
            Yes, the company should be profitable over the long term since it's net cash flow is positive. 
   
**Question 3:** The Elkhart and Western is a Class III short line in northern Indiana. However, they are running more trains than they used to. John, who lives next to the tracks and works from home, is trying to figure out how many trains he should expect to disturb him. The number of trains that passes by his house and the probabilities are listed in the table below. Calculate the expected value and standard deviation of the trains that pass by his house.

| Trains | Probability |
| ---: | :--- |
| 0 | 0.35 |
| 1 | 0.10 |
| 2 | 0.30 |
| 3 | 0.05 |
| 4 | 0.20 |

**Answer:**
$$
\mathbb{E}(Trains)=0*0.35+1*0.10+2*0.30+3*0.05+4*0.20=1.65
$$
$$
SD(Trains)=\sqrt{Var(Trains)}=\sqrt{\mathbb{E}(Trains^2)-(\mathbb{E}(Trains))^2}
$$
$$
\mathbb{E}(Trains^2)=0^2*0.35+1^2*0.10+2^2*0.30+3^2*0.05+4^2*0.20=4.95
$$
$$
SD(Trains)=\sqrt{4.95-(1.65)^2}\approx1.4925
$$
\newpage

**Question 4:** Import the Data.csv and calculate the E(X) and SD(X) of Siblings.

**Answer** 
```{r}
#Import the Data set
library(tidyverse)
Data <- read.csv("~/Desktop/DPISu22/Data Sets/Data.csv", stringsAsFactors=TRUE)
#E(X)
expected = mean(Data$Siblings)
#SD(X)
standard_deviation = sd(Data$Siblings)

#Print your solutions
expected
standard_deviation
```

## Project Questions

Feel free to work on your project if there is any time left after the labs. Paul and I are here to answer any questions during the second half of the lab times to answer mainly project related questions, but general questions are more than welcome too. Feel free to discuss among your group about any project ideas or help each other out. Remember collaboration is promoted, plagiarism is not! :)

\newpage

## Submission
Once you have finished your lab...

1. Go to the top left and click `File` and `Save`.
2. Click on the `Knit` button to convert this file to a PDF.
3. Submit **BOTH** the `.Rmd` file and `.pdf` file to Blackboard by 11:59 PM tonight.